Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Define y and R

Both Spalart--Allmaras cases did a poor job predicting the turbulence kinetic
energy in the flow, since it must be resolved as variance in the velocity field.
The 2-D SST model did a good job predicting the peak in $k$ at $y/R=-1$, though
is missing the smaller peak at $y/R=-1$. This is once again likely due to
blockage issues, where local tip speed ratio is decreased, increasing the
blades' instantaneous angle of attack at this location on the downstream
passage. In contrast, the 3-D SST model predicts the $+y$ peak in turbulence
kinetic energy very well, though the $-y$ peak magnitude is overpredicted by
about 30\%. We also see some smearing of $k$ across the center of the rotor,
which is likely due to exaggerated levels of the turbulent eddy viscosity. This
could also be an effect of mesh resolution, though for this study only base mesh
size sensitivity was assessed, rather than local refinement, as this would have
expanded the parameter space significantly.

>>>>

Both Spalart--Allmaras cases did a poor job predicting the turbulence kinetic
energy in the flow, since it must be resolved as variance in the velocity field.
The 2-D SST model did a good job predicting the peak in $k$ at $y/R=-1$, where
$y$ is the cross-stream coordinate and $R$ is the rotor radius, though is
missing the smaller peak at $y/R=-1$. This is once again likely due to blockage
issues, where local tip speed ratio is decreased, increasing the blades'
instantaneous angle of attack at this location on the downstream passage. In
contrast, the 3-D SST model predicts the $+y$ peak in turbulence kinetic energy
very well, though the $-y$ peak magnitude is overpredicted by about 30\%. We
also see some smearing of $k$ across the center of the rotor, which is likely
due to exaggerated levels of the turbulent eddy viscosity. This could also be an
effect of mesh resolution, though for this study only base mesh size sensitivity
was assessed, rather than local refinement, as this would have expanded the
parameter space significantly.
